---
title: ""
author: "JiwonMin"
date: "2017년 5월 2일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Introduction

 Major cities in the world operate public bicycle systems as green public transportation. South Korea's Daejeon City also operates a public bicycle rental system called 'Tashu' for the purpose of increasing the amount of people's exercise and distribution of public transportation demand since 2012. The system is expanding and the scale of relocation work is growing. We aim to improve the efficiency of relocation work by predicting the demand for bicycles according to factors such as weather, time, and festival.
 
 세계 주요 도시는 녹색대중교통수단으로 공공 자전거 시스템을 운영하고 있다. 남한의 대전시 또한 2012년 부터 시민들의 운동량 증대, 대중 교통 수요 분산 등을 목적으로 '타슈'라 불리는 공공 자전거 대여 시스템을 운영하고 있다. 시스템이 확대되며 재배치 작업의 규모도 커지고 있다. 기상, 시간, 축제 여부와 같은 요인에 따른 자전거 수요를 예측하여 재배치 작업의 효율성을 높이는 것을 목표로 한다.


# 2. Data
  **2.1 Tashu Station Near Park 공원 주변 정류소**
```{r}
#head(stat3_rentTrainDF,n=5)
#tail(stat3_rentTrainDF,n=5)
```
  **2.2 Tashu Station Near Residential 주거 지역 주변 정류소**
  **2.3 Tashu Station Near Company 회사 밀집 지역 주변 정류소**
  **2.4 Tashu Station Near University 대학 주변 정류소**
  **2.5 Tashu station Near Downtown 시내 주변 정류소**
  
## 3. Exploratory Data Analysis
## 4. Prediction
## 5. Result
  
  
```{r cars}
summary(cars)
```



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
