---
title: "tashu : Analysis and Demand forecast for Public bicycles('Tashu') in Daejeon, South Korea"
author: "JiWon Min"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## 1. Introduction
 The public bicycle system is spreading globally as a green public transportation. In major cities around the world, public bicycle systems are leading to the effects of distribution of public transportation demand and the increase of citizens' momentum. Through analyzing the history of bicycle rental in a city, you can check the patterns of bicycle use by citizens.By getting the time for which amount of the bike rental is increasing, it is possible to obtain a proper bike relocation work time and prevent the bicycle imbalance in advance. And By getting the mainly used routes, It can be used to select the location for new bicycle stop. This package provides bike rental history data and analysis functions of public bicycle system called 'Tashu' in Daejeon, South Korea. Bicycle rental history, stopping time information, weather data and Daejeon city festival data from 2013 to 2015 are provided  so that everyone can freely analyze patterns of bicycle use. It also provides basic analytic, statistical functions and function for prediction.


## 2. Data
1.    Tashu Data
: Bicycle rental history on Tashu from 2013 to 2015. Data is consisted of "RENT STATION, RENT DATE, RETURN STATION, RETURN DATE"
* tashu2013 : Rental history In 2013.
* tashu2014 : Rental history In 2014.
* tashu2015 : Rental history In 2015.
* tashuDataFor3year : Rental history from 2013 to 2015.

```{r}
load(file = "../data/tashu2013.rda")
head(tashu2013, n = 5)
```

2.    Tashu Station Data
: By 2014 there were 144 bicycle stations and a new one in 2015, currently operating 244 stations. In this study, only the existing data of 144 stop stations are considered. Data is consisted of "NUM(Number of station), KIOSKNUM(Number of Kiosk), DISTRICT(District where Station is located), Name(Name of station), LOCATION(Location of station), NUMOFBIKE_RACK(Number of Bike rack), GEODATA_lat(Latitude of station), GEODATA_lon(Longitude of station)"

* tashuStationData : data of 144 Stations on Tashu system. 
```{r}
load(file = "../data/tashuStationData.rda")
head(tashuStationData, n = 5)
```

3.    Weather Data
: Weather Data In Daejeon from 2013 to 2015. Data is consisted of "datetime, temperature, rainfall, windspeed, wind direction, humidity, Dew point temperature, Local Pressure, Sea surface Pressure, Sunshine, Solar Radiation, Snowfall, Ground Temperature"

* weather2013 : Weather Data In Daejeon, 2013
* weather2014 : Weather Data In Daejeon, 2014
* weather2015 : Weather Data In Daejeon, 2015

```{r}
load(file = "../data/weather2013.rda")
head(weather2013, n = 5)
```

4.    Festival Data
: Festival Data In Daejeon from 2013 to 2015. Data is consisted of "Festival(Name of festival), Location(Location of festival), nearStation(bike station affected by festival), startDate(festival starting date time), endDate(festival ending date time)"
```{r}
load(file = "../data/festivalData.rda")
head(festivalData, n = 5)
```


## 3. Analysis

대전 시민들의 자전거 사용 패턴을 확인하기 위한 분석을 수행하였다. 자전거 사용량에 영향을 주는 요인으로 시간, 기상 상태를 선정하였다. 그에 따른 자전거 사용량 변화를 확인하였다.
This package provide some functions that analyze bike usage pattern. Time and weather conditions were selected as factors affecting bicycle usage.

1.    getTop10Stations()
: This function presents top 10 stations that have most number of bike rental for 3 years.

```{r}
library(tashu)
getTop10Stations()
```

2.    getTop10Pathes()
: This function presents top 10 pathes that have mostly used for 3 years.
```{r}
library(tashu)
getTop10Pathes()
```

3.    getAmountOfRentalEachMonth()
: This function show average amount of bike rental in each months.
```{r}
library(tashu)
getAmountOfRentalEachMonth()
```

4.    getAmountOfRentalEachDayOfWeek()
: This function show bike usage pattern in each day of week.
```{r}
library(tashu)
getAmountOfRentalEachDayOfWeek()
```

5.    getUsageByTemperature()
: This function show the change of bike usage pattern according to Temperature.
```{r}
library(tashu)
getUsageByTemperature()
```


## 4. Prediction
 이 패키지는 랜덤 포레스트를 이용한 자전거 사용량 예측을 예제로 제공한다. 사용자들은 n번 정류소의 자전거 대여량을 예측하기 위해서, "학습 데이터 생성 → 예측 모델 수립 → 테스트 데이터 대입 → 예측 결과 확인" 의 과정을 거쳐야 한다.
 
 This package provides function that predict the demand of bike rental using Random Forest as example. Users must go through the process of "generating learning data → establishing a prediction model → assigning test data → confirming forecast results" in order to predict the amount of bicycle rental at the nth stop.

1.    createTrainData(stationNum)
: 이 함수는 랜덤 포레스트 예측 모델을 구현하는데 사용될 학습 데이터를 생성한다. 이 함수는 2013 ~ 2014 년도에 stationNum 정류소에서 일어난 자전거 대여 이력과 날씨, 축제 데이터를 전처리하여 다음과 같은 데이터 프레임을 만들어 반환한다.

 This function generates training data to be used to implement the random forest prediction model. This function prepares the bicycle rental history, weather, and festival data that occurred at stationNum stop in 2013 ~ 2014, and returns the following data frame. 
```{r}
#library(Tashu)
#trainData <- createTrainData(1)
#head(trainData, n = 5)
```

2.    createTestData(stationNum)
: 이 함수는 예측 모델이 예측을 하기 위한 feature 데이터를 제공하는 테스트 데이터를 생성한다. 2015년도에 stationNum 정류소에서 일어난 자전거 대여 이력과 날씨, 축제 데이터를 전처리하여 다음과 같은 데이터 프레임을 만들어 반환한다.

 This function generates testing data that provides feature data for the prediction model. Bike rental history at the stationNum th station, weather and festival data in 2015 are preprocessed and the following data frame is created and returned.
 
```{r}
#library(Tashu)
#testData <- createTestData(1)
#head(testData, n = 5)
```

3.    predictDemandOfBikesUsingRF(trainData, testData, isImportance, numOfTree, type)
: 이 함수는 trainData와 testData를 파라미터로 받아 stationNum 정류소에서의 자전거 사용량 예측을 수행한다. trainData로 랜덤 포레스트 예측 모델을 구현한다. 그 후 테스트 데이터를 예측 모델에 입력하여 자전거 사용량을 예측한다. isImportance를 TRUE로 설정할 시, stationNum 정류소에서의 feature importance를 구할 수 있다.

 This function takes the parameter trainData and testData as parameters and performs the bicycle usage prediction at stationNum stop. First, It implements the random forest prediction model with trainData and input testData to predict the demand of bike rental. If you set isImportance to TRUE, you can get the feature importance at the stationNum stop.
 
```{r}
#library(Tashu)
#trainData <- createTrainData(1)
#testData <- createTestData(1)
#
#resultData <- predictDemandOfBikesUsingRF(trainData, testData, isImportance = TRUE, numOfTree = 50, type = 1)
#head(resultData, n = 5)
```
